Type Refinements for the Working Class

### 2015-11-12 paper.tex
typos

  Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
  when the family of judgments $\mathcal{J}$ shall forevermore have a section
  (i.e. for any substitution of $\Member{\omega}{[\Omega]}$,
  $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
  \emph{valences} rather than sorts; as such, the general judgment allows us to
  quantify over terms of higher type.  However, for clarity we will often write
  $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
  $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
  the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
  proper $\MApp{\MV{m}}{\cdot}{\cdot}$.

@@

  Intuitively, the hypothetical judgment
  $\Define{\HypJ{\mathcal{J}_2}{\mathcal{J}_1}}{\mathcal{J}_1\to\mathcal{J}_2}$
  is evident when there shall forevermore be an effective transformation of the
  evidence into the evidence of the consequent. It is important to keep in mind
  that this is a \emph{semantic} consequence and therefore expresses
  admissibilities, in contrast to the the \emph{logical} consequence which
  expresses derivabilities \cite{harper:2016}. We will not have any need for
  the latter.
\end{definition}

>>>>

  Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
  when the family of judgments $\mathcal{J}$ shall forevermore have a section
  (i.e. for any substitution $\Member{\omega}{[\Omega]}$,
  $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
  \emph{valences} rather than sorts; as such, the general judgment allows us to
  quantify over terms of higher type.  However, for clarity we will often write
  $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
  $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
  the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
  proper $\MApp{\MV{m}}{\cdot}{\cdot}$.

@@

  In other words, the hypothetical judgment
  $\HypJ{\mathcal{J}_2}{\mathcal{J}_1}$ is evident when there shall forevermore
  be an effective transformation of evidence for the antecedent into evidence
  for the consequent. It is important to keep in mind that this is a
  \emph{semantic} consequence and therefore expresses admissibilities, in
  contrast to the the \emph{logical} consequence which expresses derivabilities
  \cite{harper:2016}.  We will not have any need for the latter.
\end{definition}
